Associations between Chlorophyll \emph{a} and various Microcystin-LR Health Advisory Concentrations

### 2015-09-16 manuscript/manuscript.Rmd
fixed tables

```{r microcystin_levels,echo=FALSE,results='asis', tab.cap="Various suggested microcystin-LR health advisory concentrations. \\label{tab:microcystin_levels}"}
source_of_stnd <- c("WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "U.S. EPA",
                    "U.S. EPA")
type_of_stnd <- c("Recreational",
                  "Recreational",
                  "Recreational",
                  "Recreational",
                  "Drinking",
                  "Drinking",
                  "Drinking")
concentration <- c("2-4 $\\mu$g/L",
                   "10-20 $\\mu$g/L",
                   "20-2000 $\\mu$g/L",
                   ">2000 $\\mu$g/L",
                   "1 $\\mu$g/L",
                   "0.3 $\\mu$g/L",
                   "1.6 $\\mu$g/L")
#note <- c("Low probability of adverse health effects",
#          "Moderate probability of adverse health effects",
#          "High probability of adverse health effects, These higher #concentrations typically only seen in visible scums/algal mats",
#          "Very high probability of adverse health effects",
#          "",
#          "Children younger than school age",
#          "Individuals School age and older")
mc_conc_table <- data.frame(source_of_stnd, type_of_stnd, concentration) %>%
  arrange(type_of_stnd)
names(mc_conc_table)<-c("Source","Type","Concentration")
pandoc.table(mc_conc_table,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
```

@@

```{r mc_chla_table, results='asis', echo=FALSE, tab.cap="Chlorophyll \textit{a} concentrations that are associated with a 50% probability of exceeding a microcystin-LR health advisory concentration. \\label{tab:mc_chla_table}"}
mc_chla_tbl <- data.frame(Source=mc_names,Type=mc_type,Microcystin=mc_guides,Chlorophyll=mc_chla)[1:4,]
pandoc.table(mc_chla_tbl,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
```

>>>>

```{r microcystin_levels,echo=FALSE,results='asis', tab.cap="Various suggested microcystin-LR health advisory concentrations. \\label{tab:microcystin_levels}"}
source_of_stnd <- c("WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "U.S. EPA",
                    "U.S. EPA")
type_of_stnd <- c("Recreational",
                  "Recreational",
                  "Recreational",
                  "Recreational",
                  "Drinking",
                  "Drinking",
                  "Drinking")
concentration <- c("2-4 $\\mu$g/L",
                   "10-20 $\\mu$g/L",
                   "20-2000 $\\mu$g/L",
                   ">2000 $\\mu$g/L",
                   "1 $\\mu$g/L",
                   "0.3 $\\mu$g/L",
                   "1.6 $\\mu$g/L")
#note <- c("Low probability of adverse health effects",
#          "Moderate probability of adverse health effects",
#          "High probability of adverse health effects, These higher #concentrations typically only seen in visible scums/algal mats",
#          "Very high probability of adverse health effects",
#          "",
#          "Children younger than school age",
#          "Individuals School age and older")
mc_conc_table <- data.frame(source_of_stnd, type_of_stnd, concentration) %>%
  arrange(type_of_stnd)
names(mc_conc_table)<-c("Source","Type","Concentration")
#pandoc.table(mc_conc_table,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
knitr::kable(mc_conc_table)
```

@@

```{r mc_chla_table, results='asis', echo=FALSE, tab.cap="Chlorophyll \textit{a} concentrations that are associated with a 50 percent probability of exceeding a microcystin-LR health advisory concentration. \\label{tab:mc_chla_table}"}
mc_chla_tbl <- data.frame(Source=mc_names,Type=mc_type,Microcystin=mc_guides,Chlorophyll=mc_chla)[1:4,]
#pandoc.table(mc_chla_tbl,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
knitr::kable(mc_chla_tbl)
```

### 2015-09-16 manuscript/manuscript.tex
fixed tables

\begin{longtable}[c]{@{}lll@{}}
\caption{Various suggested microcystin-LR health advisory
concentrations. \label{tab:microcystin_levels}}\tabularnewline
\toprule
\begin{minipage}[b]{0.11\columnwidth}\raggedright\strut
Source
\strut\end{minipage} &
\begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
Type
\strut\end{minipage} &
\begin{minipage}[b]{0.20\columnwidth}\raggedright\strut
Concentration
\strut\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.11\columnwidth}\raggedright\strut
Source
\strut\end{minipage} &
\begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
Type
\strut\end{minipage} &
\begin{minipage}[b]{0.20\columnwidth}\raggedright\strut
Concentration
\strut\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Drinking
\strut\end{minipage} &
\begin{minipage}[t]{0.20\columnwidth}\raggedright\strut
1 \(\mu\)g/L
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
U.S. EPA
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Drinking
\strut\end{minipage} &
\begin{minipage}[t]{0.20\columnwidth}\raggedright\strut
0.3 \(\mu\)g/L
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
U.S. EPA
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Drinking
\strut\end{minipage} &
\begin{minipage}[t]{0.20\columnwidth}\raggedright\strut
1.6 \(\mu\)g/L
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Recreational
\strut\end{minipage} &
\begin{minipage}[t]{0.20\columnwidth}\raggedright\strut
2-4 \(\mu\)g/L
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Recreational
\strut\end{minipage} &
\begin{minipage}[t]{0.20\columnwidth}\raggedright\strut
10-20 \(\mu\)g/L
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Recreational
\strut\end{minipage} &
\begin{minipage}[t]{0.20\columnwidth}\raggedright\strut
20-2000 \(\mu\)g/L
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Recreational
\strut\end{minipage} &
\begin{minipage}[t]{0.20\columnwidth}\raggedright\strut
\textgreater{}2000 \(\mu\)g/L
\strut\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{verbatim}
## Warning in split.large.cells(t): length of split.cells vector is smaller
## than data. Default value will be used for other cells
\end{verbatim}

\begin{verbatim}
## Warning in split.large.cells(t.colnames): length of split.cells vector is
## smaller than data. Default value will be used for other cells
\end{verbatim}

\begin{longtable}[c]{@{}llll@{}}
\caption{Chlorophyll extit\{a\} concentrations that are associated with
a 50\% probability of exceeding a microcystin-LR health advisory
concentration. \label{tab:mc_chla_table}}\tabularnewline
\toprule
\begin{minipage}[b]{0.11\columnwidth}\raggedright\strut
Source
\strut\end{minipage} &
\begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
Type
\strut\end{minipage} &
\begin{minipage}[b]{0.17\columnwidth}\raggedright\strut
Microcystin
\strut\end{minipage} &
\begin{minipage}[b]{0.17\columnwidth}\raggedright\strut
Chlorophyll
\strut\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.11\columnwidth}\raggedright\strut
Source
\strut\end{minipage} &
\begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
Type
\strut\end{minipage} &
\begin{minipage}[b]{0.17\columnwidth}\raggedright\strut
Microcystin
\strut\end{minipage} &
\begin{minipage}[b]{0.17\columnwidth}\raggedright\strut
Chlorophyll
\strut\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
U.S. EPA
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Drinking
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
0.3
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
23.68
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Drinking
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
1
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
63.94
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
U.S. EPA
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Drinking
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
1.6
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
89.71
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Recreational
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
2
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
102.6
\strut\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

>>>>

\begin{longtable}[c]{@{}lll@{}}
\caption{Various suggested microcystin-LR health advisory
concentrations. \label{tab:microcystin_levels}}\tabularnewline
\toprule
Source & Type & Concentration\tabularnewline
\midrule
\endfirsthead
\toprule
Source & Type & Concentration\tabularnewline
\midrule
\endhead
WHO & Drinking & 1 \(\mu\)g/L\tabularnewline
U.S. EPA & Drinking & 0.3 \(\mu\)g/L\tabularnewline
U.S. EPA & Drinking & 1.6 \(\mu\)g/L\tabularnewline
WHO & Recreational & 2-4 \(\mu\)g/L\tabularnewline
WHO & Recreational & 10-20 \(\mu\)g/L\tabularnewline
WHO & Recreational & 20-2000 \(\mu\)g/L\tabularnewline
WHO & Recreational & \textgreater{}2000 \(\mu\)g/L\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[c]{@{}llrr@{}}
\caption{Chlorophyll extit\{a\} concentrations that are associated with
a 50 percent probability of exceeding a microcystin-LR health advisory
concentration. \label{tab:mc_chla_table}}\tabularnewline
\toprule
Source & Type & Microcystin & Chlorophyll\tabularnewline
\midrule
\endfirsthead
\toprule
Source & Type & Microcystin & Chlorophyll\tabularnewline
\midrule
\endhead
U.S. EPA & Drinking & 0.3 & 23.68\tabularnewline
WHO & Drinking & 1.0 & 63.94\tabularnewline
U.S. EPA & Drinking & 1.6 & 89.71\tabularnewline
WHO & Recreational & 2.0 & 102.60\tabularnewline
\bottomrule
\end{longtable}
